Understanding GDP relations to Crime in US Cities

### 2017-03-07 resource/index.Rmd
making long format for gdp and crime

---
title: "Understanding the Affects of GDP and Population on Crime in US Cities"
output: html_notebook
---
&nbsp;

#### Isabella Spaletta, Marisa Nanakul, Christopher Ross, Kai Yoshino
##### Affiliation: University of Washington - Information School
&nbsp;

### Purpose

>>>>

---
title: "Understanding GDP relations to Crime in US Cities"
author: "Kai Yoshina, Isabella Spaletta, Chrisopther Ross, Marisa Nanakul"
date: "March 6, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("resources.R")
```

### What is the data?

The data that we used in this anaylsis is combination of a data set that has crime in US cities over a 5 year time persion (2010-2015) and the GDP for cities in the same time period.
